学術論文

### 2023-05-26 articles.Rmd
update

- [44] Hamatani, S., Matsumoto, K., Kunisato, Y., Okawa, S., Yamashita, M., Mizuno, Y. (in press) Dismantling cognitive-behavioral therapy components for attention-deficit hyperactivity disorder in adolescents and adults: protocol for a network meta-analysis. BMJ Open

>>>>

- [45] Toyama, A., Katahira, K., Kunisato, Y. (in press). Examinations of Biases by Model Misspecification and Parameter Reliability of Reinforcement Learning Models. Computational Brain & Behavior

- [44] Hamatani, S., Matsumoto, K., Kunisato, Y., Okawa, S., Yamashita, M., Mizuno, Y. (in press). Dismantling cognitive-behavioral therapy components for attention-deficit hyperactivity disorder in adolescents and adults: protocol for a network meta-analysis. BMJ Open
